### 2012-11-25 paper.tex
asdf
bla

\paragraph{}It should be clear that the variables ``survival'' and ``still-alive'' should not be used for classification since they constitute the final prediction attribute. Listing \ref{lst:silly-tree} shows what happens if a decision tree can take these attributes into account. It states that if the patient survived $ <= 12 $ months, he survived at least 12 month. Pretty accurate, right? 
The only remarkable thing is, that the J48 implementation under default settings seems to enforce a certain depth of the tree, even if the splitting on the same attribute is redundant since $ x > 11 \rightarrow x > 12 $.

\begin{lstlisting}[caption={Decision tree on 100\% dependant attributes}, label=lst:silly-tree, float=htb]
J48 pruned tree
------------------
    survival <= 12
    |   survival <= 11: 0 (4.0)
    |   survival > 11: 1 (4.0)
    survival > 12: 1 (87.0)
\end{lstlisting}

@@

\subsection{Random Forest}

>>>>

%\paragraph{}It should be clear that the variables ``survival'' and ``still-alive'' should not be used for classification since they constitute the final prediction attribute. Listing \ref{lst:silly-tree} shows what happens if a decision tree can take these attributes into account. It states that if the patient survived $ <= 12 $ months, he survived at least 12 month. Pretty accurate, right? 
%The only remarkable thing is, that the J48 implementation under default settings seems to enforce a certain depth of the tree, even if the splitting on the same attribute is redundant since $ x > 11 \rightarrow x > 12 $. 
%
%\begin{lstlisting}[caption={Decision tree on 100\% dependant attributes}, label=lst:silly-tree, float=htb]
%J48 pruned tree
%------------------
%    survival <= 12
%    |   survival <= 11: 0 (4.0)
%    |   survival > 11: 1 (4.0)
%    survival > 12: 1 (87.0)
%\end{lstlisting}

@@

\subsubsection{Random Forest}
